### 2019-09-03 README.Rmd
add task diplodia

- Task "ecuador" -> `mlr_tasks$get("ecuador")`

@@

```{r spcv-coords-all-partitions}
library(mlr3)
library(mlr3spatiotemporal)
task <- tsk("ecuador")
resampling = rsmp("spcv-coords")
resampling$param_set$values = list(folds = 5)
resampling$instantiate(task)

>>>>

- Task "ecuador" -> `mlr_tasks$get("ecuador")`
- Task "diplodia" -> `mlr_tasks$get("diplodia")`

@@

```{r setup, include=FALSE}
set.seed(123)
```

```{r spcv-coords-all-partitions}
library(mlr3)
library(mlr3spatiotemporal)
library(ggplot2)

task <- tsk("ecuador")
resampling = rsmp("spcv-coords")
resampling$param_set$values = list(folds = 5)
resampling$instantiate(task)
